% Mitchell Hopkins's CV
% Last revision 6th Oct 23

\documentclass[10pt,a4paper]{article}

% environments
\newenvironment{indentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
	\item[]%
}
{\end{list}}

\newenvironment{unindentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{-0.5#1}}%
	\item[]%
}
{\end{list}}

% commands
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

% set font
\usepackage[OT1]{fontenc}
\renewcommand*\familydefault{\sfdefault}

% packages to be used
\usepackage{fancyhdr}
\usepackage[margin=1.25in]{geometry}
\usepackage{hyperref}
    \hypersetup{colorlinks=true,linkcolor=RoyalBlue,urlcolor=RoyalBlue}
\usepackage{multicol}
\usepackage[dvipsnames]{xcolor}

\hyphenpenalty=1000
\exhyphenpenalty=1000


% section parameters
\usepackage{titling}
\usepackage{titlesec}
    \titleformat{\section}{\color{darkgray}\Large\scshape\bfseries}{}{0em}{}
    \titleformat{\subsection}{\scshape\bfseries}{}{0em}{}
    \titleformat{\subsubsection}[runin]{\bfseries}{}{0em}{}
    \titlespacing{\section}{0em}{-.8em}{0em}
    \titlespacing{\subsection}{0em}{-.2em}{0em}
    \titlespacing{\subsubsection}{2em}{-.2em}{.5em}

\begin{document}

% header and footer
\fancypagestyle{firstpage}
{
	\fancyhf{}
	\setlength\headheight{43pt}
	\fancyhead[LO,LO]{\color{darkgray}\bfseries\Large{{Mitchell Hopkins}} \\ \small{\href{mailto:mh@artydh.io}{mh@artydh.io} | \href{https://linkedin.com/in/artydh}{LinkedIn} | ({+}44) 77633 51192}}
	\fancyfoot[CO]{}
}

\thispagestyle{firstpage}
\vspace*{-2.5em}

% document content
\section{Summary}
\begin{multicols}{2}
    \noindent \emph{\color{gray}\small A creative technologist with a passion for learning, evolving and maintaining high standards of work.}\\\\
    \noindent An IT professional has been driven by a desire to grow, improve and enrich not only myself but also my colleagues. I strongly believe in sharing knowledge and information through excellent communication and team-work. I possess good time management skills, creativity and an attention to detail that enables me to problem solve, getting to the issues at hand. My creativity allows me to think ``outside of the box'', also helping to see the bigger picture as well as the more fine-grained.\\

    \noindent Having an academic background, I am analytical and methodical, allowing me to understand complex problems. Through my proficiency in English and great communication skills I am able to provide, question and format information in a clear, concise manner. 
\end{multicols}

\hrule
\vspace*{2em}

\section{Experience}

\begin{itemize}
	\parskip=0.1em

	\item
	\headerrow
		{\textbf{Ideal World Limited}}
		{\textbf{Peterborough, UK}}
	\\
	\headerrow
		{\emph{IT Operations Analyst}}
		{\emph{May '23 -- Oct '23}}
	\begin{itemize}
		\item Job title change, duties continued from previous position.
		\item I was responsible for modernising the company's intranet/internal sites using Sharepoint 365. Until this point, we had been running on Sharepoint 2010. I redesigned the pages meticulously while consulting stakeholders across all departments of the business whilst ensuring that no data was lost in the final switch-off of the old on-premise server.
		\item The IT team performed a datacenter move in the middle of May. I was responsible for logging, tracking and announcing issues to the wider team so that they could focus on their tasks on the day of migration. I originally designed a system within Microsoft Teams using Kanban boards, which exposed me to Power Automate and Power Apps, creating automation flows where the team could report issues as they occured with minimal interruption to their tasks. Unfortunately, this method did not gel with some members of the team and I then moved to using Azure DevOps Boards where we tracked issues in an Agile/Scrum style. I became highly interested in the Agile methodology and due to this and am looking at pursuing certification in Agile/Scrum.
		\item I rewrote and updated the company's IT Security Policy, with the assistance of a colleague and with the guidance of the Head of Finance, to ensure that rules and guidelines were clear, being designed to minimise any potential data loss that would be cause for concern under PCI-DSS regulations.
		\item The company filed for administration in early June and as part of this process, I was responsible for ensuring the correct and proper handling of company data on user devices as well as assisting with queries from the Infrastructure team and our Business Analyst.
	\end{itemize}

	\item
	\headerrow
		{\textbf{Ideal World Limited}}
		{\textbf{Peterborough, UK}}
	\\
	\headerrow
		{\emph{Service Desk Analyst}}
		{\emph{June '21 -- May '23}}
	\begin{itemize}
		\item In this role, I was tasked with resolving first, second and, on occasion, third-line support tickets into the IT helpdesk. These tickets ranged from assisting with computer peripherals and desk setups to working with both the Application and Infrastructure Support teams to ascertain the cause of a complex issue.
		\item During my time in this role, I was exposed to many new technologies and software. These included Active Directory, SCCM and Azure. I also became adept at Office 365 administration and routinely assisted users with varying issues, such as problems with OneDrive, Outlook and Windows 10/11.
		\item I also gained knowledge of Microsoft Teams administration and helped to roll out a company-wide Teams Calling VoIP solution. I was responsible for ensuring that call queues were correct, DDIs were assigned to staff members and upgrading our meeting rooms by installing Teams-capable devices for conference calls.
		\item I had the opportunity to assist in running SQL queries under the supervision of the Application Support team. The queries I was running were to ensure that manual payments taken from customers were correctly written off against their accounts. This included running reports to ensure that the information provided by the customer experience team(s) was correct and running a query to update the status of the refund on the customer's account. This experience interested me deeply and I have been self-studying SQL and data analysis since.
	\end{itemize}

	\item
	\headerrow
		{\textbf{Ideal Shopping Direct Limited}}
		{\textbf{Peterborough, UK}}
	\\
	\headerrow
		{\emph{Returns Specialist}}
		{\emph{2019 -- 2021}}
	\begin{itemize}
        \item Ideal Shopping Direct Limited was an omni-channel retailer, focussed primarily on TV shopping. The company's subsidaries were UK household names and included Ideal World and Create and Craft.
		\item In this role, I was part of a team of three colleagues tasked with performing quality assurance checks on customer returns. Chiefly, these returns were technology and jewellery. This included arranging repair services with product suppliers, performing maintenance on items to assist customers and providing refunds/replacements where necessary.
		\item As part of this role, I overhauled the way in which the team tracked items sent to repair using an Excel spreadsheet with basic VBA macros for auto-logging of time and date, automatic formatting of cells based on multiple criteria and enhancing the ``repair sheet'' sent to repairers to make information more accessible and clear.
	\end{itemize}

	\begin{center}
		\color{gray}\small\emph{A full work history is available on my \href{https://linkedin.com/in/artydh}{LinkedIn profile}.}
	\end{center}
\end{itemize}
\vspace{-0.5em}
\hrule
\vspace{1.75em}
\section*{Education}

\begin{itemize}
	\parskip=0.1em

	\item 
	\headerrow
		{\textbf{University College London}}
		{\textbf{London, UK}}
	\\
	\headerrow
		{\emph{MA Linguistics with a Specialisation in Pragmatics}}
		{\emph{2019 -- 2020}}
	\begin{itemize}
		\item Graduated with Merit.
		\item Notable: A short course on Natural Language Processing and Machine Learning which sparked an interest in data science and artificial intelligence.
		\item Modules included: Neurolinguistics, Syntax \& Advanced Pragmatic Theory.
	\end{itemize}
    \item 
	\headerrow
		{\textbf{University of Brighton}}
		{\textbf{Brighton, UK}}
	\\
	\headerrow
		{\emph{BA(Hons) Linguistics}}
		{\emph{2016 -- 2019}}
	\begin{itemize}
		\item Graduated with First.
		\item Modules included: Psycholinguistics \& Pragmatics.
	\end{itemize}
\end{itemize}

\hrule
\vspace{1.75em}

\section*{Skills}
\subsection*{Technical}
\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{description}
	\item[Computer Languages:]
	Basic-intermediate SQL, HTML/CSS, Markdown, basic \LaTeX.
    \item[Technologies:]
    Azure, 365, AD, Sharepoint, Windows 10/11, macOS, basic Linux CLI.
\end{description}
\end{indentsection}
\subsection*{Non-Technical}
\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{description}
	\item[Natural Languages:]
	English (Native), Greek (Beginner)
    \item[Other:]
    Communication, time management, organisation, analysis.
\end{description}
\end{indentsection}
\vspace{2em}
\begin{center}
    \color{gray}\small\emph{References available upon request.}
\end{center}
\thispagestyle{empty}
\end{document}